\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-02-05 paper/ms.tex
update paper

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
\begin{verbatim}
import numpy as np
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

        \begin{figure}[!htb]
            \includegraphics[scale=.4]{figs/tpf-plot.pdf}
            \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
            \caption{Displaying a given frame of a TPF using \texttt{plot}.
            Optionally, an \texttt{aperture\_mask} can be passed which is
            highlighted on the right hand side.}
            \label{fig:plot-method}
        \end{figure}

@@

Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

The mathematical structure of the cost function is a direct consequence of
the statistical assumptions made for data.

The following cost function is often used
\begin{align}
    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \sum_{t}|f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)|^p, p>0, p \in \mathbb{R},
\end{align}
in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.

@@

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from lightkurve.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

In this setting, the user is left to choose the cost function and the number
of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].

The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}).

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

@@

For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
The selection of the number of CBVs is also done empirically by inspecting the
grid search curve.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

@@

\begin{verbatim}
from lightkurve import KeplerTargetPixelFile
from lightkurve.psf import PRFPhotometry, SceneModel
from oktopus import UniformPrior

tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
prf = tpf.get_prf_model()
prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
scene = SceneModel(prf=[prfs])

phot = PRFPhotometry(scene_model=scene, prior=prior)
results = phot.fit(tpf.flux + tpf.flux_bkg)
\end{verbatim}

>>>>

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
\begin{verbatim}
>>> import numpy as np
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
>>> tpf.plot()
>>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.4]{figs/tpf-plot.pdf}
    \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
    \caption{Displaying a given frame of a TPF using \texttt{plot}.
    Optionally, an \texttt{aperture\_mask} can be passed which is
    highlighted on the right hand side.}
    \label{fig:plot-method}
\end{figure}

@@

Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs. The mathematical
structure of the cost function is a direct consequence of the statistical
assumptions made for data.

For instance, if one assumes that the data comes from an independent and
identically distributed (iid) multivariate Gaussian distribution with mean
$\sum_{j=1}^{n}\theta_j v_{j}(t)$ and known variance $\sigma^2$, then the
cost function can be expressed as follows
\begin{align}
    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t}\left(f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right)^2,
\label{eq:chi-square}
\end{align}
in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.

The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{*}}$ can be
expressed as
\begin{align}
    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta}
    \mathcal{C}(\bm{\theta}, f_{SAP}).
\end{align}

However,~(\ref{eq:chi-square} is known to be sensitive to outliers [add reference],
therefore, as a default behaviour in \texttt{lightkurve}, we use the following cost
function
\begin{align}
    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert,
\label{eq:l1-norm}
\end{align}

@@

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
(Tabby's star) can be written as follows
\begin{verbatim}
>>> from lightkurve.lightcurve import KeplerCBVCorrector
>>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
    ...                          "0084/008462852/kplr008462852-2011073133259_llc.fits")
>>> cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}
Fig~\ref{fig:cbv-correction} illustrates the correction.

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.pdf}
    \caption{CBV correction applied on \texttt{KOI 8462852}}
    \label{fig:cbv-correction}
\end{figure}

@@

As an example, Fig.~\ref{fig:cbv-correction-k2} illustrates the result after
estimating the first nine coefficients for CBV correciton on target
\texttt{EPIC 201543306}.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
    \label{fig:cbv-correction-k2}
\end{figure}

\subsubsection{Number of CBVs}
The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}), which shows the cost
function as a function of the number of CBVs. Usually, as the number of
CBVs increases, the value of the cost function decreases. And therefore,
the user should empirically choose a number of CBVs which does not
remove the astrophysical signal of interest [add reference].
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

An objective way of selecting the number of CBVs is to use Bayes' factors
[add reference]. In the Bayes' factor setting, the selected number of
CBVs is the one that provide the least gain in posterior probability, i.e.,
for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
as follows
\begin{align}
    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
\end{align}
in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
Estimator (MAP) obtained using $n$ CBVs.

A Laplacian prior with zero mean and variance $16$ is the default prior
density over the CBVs coefficients.

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-bayes-factor.pdf}
    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
    \label{fig:cbv-grid-search}
\end{figure}

@@

\begin{verbatim}
>>> from lightkurve import KeplerTargetPixelFile
>>> from lightkurve.psf import PRFPhotometry, SceneModel
>>> from oktopus import UniformPrior
>>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
>>> prf = tpf.get_prf_model()
>>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
>>> scene = SceneModel(prf=[prfs])
>>> phot = PRFPhotometry(scene_model=scene, prior=prior)
>>> results = phot.fit(tpf.flux + tpf.flux_bkg)
\end{verbatim}
